Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2022-03-10 doc/peakcharacterization_manuscript.Rmd
whoops, wrong thing to print
update to the manuscript to have better figures

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE, 
                      dpi = 600, 
                      dev = "png", 
                      dev.args = list(type = "cairo"),
                      fig.process = dn_modify_path)
```

@@

```{r rsd_table, results = 'asis'}
tar_load(rsd_values)
knitr::kable(rsd_table_rsd_data, digits = 3)
```

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE, 
                      fig.width = 8, 
                      fig.height = 6, 
                      fig.process = dn_modify_path,
                      dpi = 600,
                      dev.args = list(png = list(type = "cairo")))
```

@@

```{r rsd_table, results = 'asis'}
tar_load(rsd_values)
knitr::kable(rsd_values, digits = 3)
```
